---
title: "Framing Effects in the Wild"
author: "Nicolai Berk"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: false
    fig_caption: yes
    includes:
      in_header: preamble.tex
# subtitle: Manuscript prepared for the 12th Annual Conference of the European Political Science Association in Prague, Czech Republic
fontsize: 12pt
geometry: margin=1.5in
abstract: "Does news framing affect public opinion? While a large body of experimental work suggests that individual attitudes can be easily altered by emphasizing different aspects of an issue, little is known about how these studies translate into the real world. I exploit a rare change in the migration framing of the major German tabloid *Bild* to study whether experimental estimates of framing effects translate into the real world. In a first step, I develop a framework for the measurement of emphasis frames in political communication using supervised machine learning. Using this framework, I show that the emphasis of crime in *Bild*'s migration coverage severely increased. Second, I employ a difference-in-differences design using panel data from over 16,000 individuals in ten waves to assess the precise impact of this shift on migration attitudes. The findings show that, despite a major change in migration framing, a clear null effect on immigration attitudes and related variables can be observed. Tracing three key assumptions underlying the translation of experimental effect estimates suggests that news framing affects attitudes only within limited windows of opportunity early in the politicization of political issues."
bibliography: C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib
nocite: |
  @CologneReport2016
---

```{r setup, include = F}

knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, fig.width=10, fig.align='center', eval = T)


library(tidyverse)
library(dplyr)
library(data.table)
library(fixest)
library(lubridate)
library(patchwork)
library(here)



# load self-made functions
for (filename in list.files(here("code/functions"))){
  source(here(paste0('code/functions/', filename)))
}

```

WORD COUNT: `r wordcountaddin::word_count(here("paper/Manuscript_Framing.Rmd"))`

*I am thankful for extensive feedback and other support on this manuscript from Christian Arnold, Daniel Bischof, Philipp Broniecki, Jóhanna Ýr Bjarnadóttir, Elias Dinas, Florian Foos, Violetta Haas, Felix Hagemann, Julian Heid, Christina Gahn, Heike Klüver, Martin Vinæs Larsen, Matthew Levendusky, Will Lowe, Thomas M. Meyer, Rune Slothuus, Judith Spirig, Antonio Valentim as well as participants of CompText 2022, EPSA 2022, ICA 2022, EPSIP Colloquium at HU Berlin, CIVICA EGN Workshop at the EUI,  and the Political Behaviour Section at Aarhus University. I also thank the two RAs, Robin Groß and Nathalie Aerts, for annotating the news articles. All remaining confusions are my own.*

# Introduction: Does Framing Matter?

Does news framing affect public opinion? While a large body of experimental evidence suggests that the emphasis of a certain consideration can substantially alter issue attitudes, we know little about the translation of these findings into real-world environments. Prior work has shown that the external validity of such experiments might be seriously complicated by the current salience and politicisation of the issue of interest [@Arceneaux2009; @Bechtel2015; @Lecheler2009a], the availability of different frames [@Chong2007; @Chong2013; @Druckman2003; @Druckman2012] and communicating actors [@Slothuus2010], as well as the seeking and avoidance of specific content [@Lau2021a; @Taber2006]. Contemporary news environments provide consumers with especially diverse content and maximize their abilities to choose specific outlets and avoid others [@Bennett2008], thereby increasing the gap between the real-world environment and experimental studies. Additionally, the very nature of experiments is prone to over-estimate effects in the real world [@Barabas2010]. This is the reason why, fifteen years ago, Donald Kinder called for framing research to extend its toolkit: "[E]xperimental results can always be questioned on their generalizability, and framing effects are no exception. [...] A more balanced reading of frame effects requires methodological diversification, experiments and studies oriented to the world outside" [-@Kinder2007, 157].

In this article, I provide the - to my knowledge - first observational estimate of framing effects by exploiting a rare shift in the framing of a highly politicized issue - migration - in Germany's largest tabloid newspaper, *Bild*. The case is ideal to assess the everyday influence of issue frames on public opinion, as one outlet substantially changed its framing while other papers maintained theirs. Providing a novel framework for the measurement of emphasis frames using BERT models, I study migration framing in a corpus of 2.5 million newspaper articles. I show that the newspaper's migration coverage saw a strong increase in the use of crime frames after the editor in chief was replaced. The fielding of the German Longitudinal Election Study in the same period provides the rare opportunity to precisely assess the effect of framing on political attitudes using a *difference-in-differences (DiD) design*.

The results indicate that even a strong increase in the use of crime frames did not affect consumers' immigration attitudes. The estimated effect is statistically indistinguishable from zero and significantly smaller than even minimally relevant effect magnitudes. Related issue attitudes, voting behavior, and issue importance are similarly unaffected, as is the association of immigration attitudes with the frame provided. Tracing different assumptions underlying the translation of experimental estimates of framing effects into the real world implies that this lack in responsiveness is not an outcome of readers abandonment of the newspaper, nor the "crowding out" of information through other sources, but rather the crystallization of immigration attitudes prior to the change in framing. 

Overall, these findings fundamentally challenge the external validity of a large body of framing effects research and suggest that the influence of individual news outlets on public opinion is more limited than previously thought. Even a strong change in news framing did not affect political attitudes. Instead, it seems that the news media faces limited windows of opportunity to shape public opinion during the politicization of novel political issues.

# Framing Effects on Public Opinion {#framing-effects}

"Framing is the process by which a communication source, such as a news organisation, defines and constructs a political issue or public controversy" [@Nelson1997Rally]. Different forms of frames have been conceptualized. When I talk about 'frames' here, I refer to *emphasis frames*. These frames emphasize certain topics in relation to an issue, guiding the recipient to think about the issue with those considerations in mind that are promoted by the frame [@Leeper2020, 152]. Many other forms of framing exist, such as equivalence frames [@Kahneman1979prospect], episodic frames [@Iyengar2005], or generic frames [@DeVreese2005]. The focus on emphasis frames in this study is owed to the generalized theory regarding their effect on attitudes about any issue (as opposed to generic and episodic frames), as well as their common use in news content (which is not the case for equivalence frames). 

Work using the emphasis framing concept of framing mostly builds on the expectancy-value model developed by @Ajzen2000. This model suggests that an attitude on a given issue is a function of two things: the value of considerations relating to that issue and the strength of their association with the issue. The evaluation of the issue is subdivided into a number of considerations, which will carry clear evaluations. For example, to form an opinion about whether immigration to one's country should be restricted, a person might consider the humanitarian conditions in the countries of origin (negative consideration regarding restrictive migration policy), as well as the risk of increased crime (positive consideration; note that the model does not differentiate whether a consideration is grounded in objective reality). Individuals weigh each of these considerations (so-called "frames in thought"; @Druckman2001) to form an overall opinion on the subject. 

Figure \ref{fig:cogStor} visualizes this logic. A given issue (bottom square) carries an attitude $y$. The issue is associated with a number of different considerations (top circles), each of which carries an evaluation $x_i$, e.g. crime is viewed very negatively. Based on the strength of the association $w_i$ of a given consideration with the issue, a given consideration's evaluation is more or less reflected in the overall attitude $y$, which is equal to the weighted sum of considerations. For example, if a given individual associates immigration strongly with an increase in criminal activity, welfare fraud, but only very weakly with humanitarian considerations, cultural enrichment, liberty, or economic growth, they will form a rather negative attitude about the issue, as the former factor more prominently in their reasoning about migration.

```{=tex}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{vis/CognitiveStorage.png}
    \caption{The cognitive evaluation of an issue $y$ is determined by the strength of association $w_i$ with other concepts with existing evaluations $x_i$.}
    \label{fig:cogStor}
\end{figure}
```

How does this model incorporate news content and other forms of political communication? News content can emphasize different considerations of an issue (so-called "frames in communication"). By being exposed to the consideration, an individual's cognitive association of the issue at hand with the raised consideration strengthens (or in more technical terms: the weight of the consideration $w_i$ increases). As a result, this specific consideration factors more prominently in the formulation of an overall attitude: "media frames influence opinions by stressing specific values, facts, or other considerations, endowing them with greater apparent relevance to the issue than they might appear to have under an alternative frame" [@Nelson1997Rally, 569].

Applying this to the issue of migration policy and the consideration of criminal migrants, one can imagine a news consumer confronted with an increased volume of news about crimes committed by migrants. The value-expectancy model predicts that 1) the consumer forms a cognitive definition of migration that is increasingly associated with the issue of crime, meaning this consideration features more prominently when forming an opinion about the appropriate level of immigration; 2) as a result, their opinion about migration policies should become more restrictive, as the negative consideration of crime is weighted more heavily in the evaluation of the migration issue.

***Association hypothesis*****: When an individual is exposed more to a specific consideration about an issue, their association of the issue with this consideration should be strengthened.**

***Evaluation hypothesis*****: When an individual is exposed more to a specific positive/negative consideration about an issue, their attitude about the overall issue should become more positive/negative.**

# Limits of Framing Experiments {#framing-limits}

Research on framing has shown for decades that citizens' attitudes and their issue associations are highly reactive to minor changes in the emphasis of specific considerations [@Chong2007b; @Chong2010; @Druckman2012Bias; @Kinder1990; @Nelson1996; @Nelson1997Rally; @sniderman2004structure; for reviews see @Busby2019; @Druckman2001; @Leeper2020]. However, it remains unclear how well these experimental findings translate into the real world. Below, I outline three key assumptions in the translation of experimental estimates. 

First, taking experimental effects as estimates of the real-world impact of framing means making strong assumptions about citizens' exposure to frames: while framing studies usually simply present news articles or other forms of political content to respondents, news content in the real world competes with other news and entertainment content to reach its audience. Changes in news framing itself might affect how likely readers are to consume news content: readers might be less likely to consume frames challenging their existing attitudes and reject news content containing such frames (and vice versa seek out attitudinally congruent information). This idea of 'selective exposure/avoidance' [@Bennett2008], or a 'confirmation bias' [@Taber2006] brings with it a major endogeneity problem making purely correlational evidence of framing effects rather uninformative. As most framing studies do not offer choice of content to respondents, engagement remains an assumption when taking experimental studies as evidence of framing effects in the real world [for an exception see @Druckman2012Bias]. 

Second, even if consumers receive the content, it is not clear how much an individual relies on this source when forming an opinion on the subject.  Information from different sources - such as TV, newspapers, social media, or alternative online media - might 'crowd out' the framing of a single outlet: by consuming content from many sources, individuals might give less attention to a given source, thereby severely limiting the overall impact of that outlet's coverage. Experimental evidence suggests that, when an individual receives competing frames, these cancel each other out, although the precise impact is dependent on the relative timing of exposure, the quality of the frame, as well as individual characteristics [@Chong2007b; @Chong2010; @Chong2013].

Third, cognitive engagement with frames might strongly differ in the real world compared to experimental contexts. Once individuals formed political attitudes, they might resist framing: Motivated reasoners presented with a plethora of news content about an issue will spend less time and cognitive energy on counter-attitudinal arguments than those supporting their viewpoint, lending more importance to considerations raised by amenable content [@Taber2006]. Experimental evidence suggests similar dynamics specifically for framing: when individuals are free to choose content, initial frames dominate the opinion-formation process, while novel frames are rejected [@Druckman2012Bias] and even serve to strengthen pre-existing attitudes [@Bechtel2015]. This also explains why citizens are less reactive to framing attempts on salient and politicized issues [@Lecheler2009b].

In sum, there are many reasons to assume that framing might have very different consequences in real-world environments than in their experimental emulations. If one takes experimental evidence as an approximation of the effectiveness of framing in the real world, they make many strong assumptions about citizens' exposure to, reliance on, and cognitive engagement with the frames in news content. Experiments can only incorporate few characteristics of the real world at a time. In order to test the external validity of framing effect studies, it is necessary to study observational data.

# Existing Observational Studies of Framing Effects

Despite repeated calls for the assessment of framing effects beyond experimental studies [@Busby2019; @Kinder2007; @Leeper2020], there is little research addressing this concern. While a large body of observational media effects research exists, it has not paid specific interest to framing, instead assessing the impact of changing news exposure on issue attitudes and voting behavior more broadly. Most of these studies are concerned with exposure to a different outlet [@Bail2018; @Broockman2022; @Foos2022; @Grossman2022; @Guess2021]. This is problematic, as citizens are often aware of outlets' political slant and engage with the coverage differently [@Baum2008; see also @Spirig2020 for a discussion of this issue]. The existing studies focusing on within-outlet changes in coverage do not identify changing framing directly and assess effects on a broad set of dependent variables, rather than specific issue attitudes [@Levendusky2022; @Spirig2020].

The precious small body of existing observational research specifically about framing is often riddled with endogeneity issues. For example, @Jerit2008 investigates the effects of news framing on public opinion. She finds that framing is less effective in affecting public opinion compared to engagement with opposing considerations, a finding that suggests that framing is rather ineffective. Others show with similar designs that only specific frames seem to drive issue importance [@Mclaren2018], but do not assess effects on attitudes. However, these studies restrict themselves to the assessment of correlational evidence. This is especially problematic regarding framing effects, as news content can affect consumers' inclination to consume news (see preceding section), and political actors might react to public opinion. As both variables affect each other at the same time (endogeneity), it is impossible to assess which direction causality runs.

To my knowledge, there are only two observational studies assessing the causal effect of exposure to specific content on political attitudes. @Slothuus2010b takes advantage of a sudden shift in a political parties' framing of retirement benefits, and shows that this changed framing has substantial impact on party supporters' attitudes about the issue. However, given that a positional change coincided with the changing framing of the issue and parties' special role in citizens' information process, one cannot distinguish the effect of partisan cue-taking from the persuasive effect of the frame itself. Additionally, it is unclear how these findings translate from parties' communication to news framing effects.

The only study which - to my knowledge - assesses the precise impact of changing news content on political attitudes comes from @Djourelova2020. She exploits a ban of the term "illegal migrant" in the *Associated Press* and shows that this language has modest effects on migration attitudes. While the study itself reveals impressively how language can shape political attitudes, it constitutes a highly specific case and a rather minor change in the framing of migration. To gain a deeper understanding of how specifically *framing* affects immigration attitudes, it is necessary to assess broader changes in the representation of the immigration issue.

It becomes obvious that the discipline lacks an understanding of how news framing affects political attitudes in the real world. While experimental studies find strong effects, several assumptions have to be made to translate them beyond the lab or survey context. Observational evidence on media effects has not precisely studied the impact of framing. To do so, it is necessary to assess within-outlet changes in news framing and their effect on specific issue attitudes using a design able to identify causal effects. The following section therefore presents a research design building on a rare change in the migration framing in Germany's largest tabloid, *Bild*. It then develops a framework to measure emphasis framing in political communication, and presents a panel dataset tracking migration attitudes in the time-frame of interest, as well as a *difference-in-difference* design to estimate the causal effect of the changing framing. The final section discusses the expected effect size from experimental studies, in order to provide a baseline for comparison.

# Research Design

In order to test whether changing news content affected political attitudes, I exploit an editorial change in the largest German newspaper, *Bild*. As I will show, this editorial change resulted in a substantial shift in the papers' migration framing and is hence ideal to assess the effect of within-newspaper content shifts. The fielding of a large-scale panel survey in the same period allows to assess the precise impact of this change in news content on consumers' migration attitudes.

## A Rare Shift in Migration Framing

In the summer of 2015, Germany became sanctuary for around 800,000 refugees who had fled war, violence, and famine in Syria and elsewhere. The German public debated how to deal with the newly arriving and for the first time since the post-war years, a radical right party was likely to win representation in the national parliament. Surprisingly, given its traditional populist style and right-wing takes on migration, the major tabloid newspaper *Bild* initially maintained a somewhat balanced coverage of the newly arriving, which - although portraying migrants more negatively than other outlets - even started a campaign called "#RefugeesWelcome" to gather support for the newly arriving [@Maurer2019; see @BildRefugeesWelcome]. This was often connected to chief editor Kai Diekmann, who hosted a refugee family in his home [@BR2015Diekmann].

In December 2016, Axel Springer, the company owning Bild, announced that Diekmann will leave the company. Less than a week after, it became public that prosecutors investigate Diekmann for sexual harassment. While the company claimed that this was not the reason for Diekmann's departure, the process might have been sped up as a result of the investigations\footnote{According to a former editor of the newspaper I talked to, rumors in the company at the time support this interpretation of events.} [@Spiegel2017Diekmann]. The migration coverage in *Bild* severely changed when Diekmann left the newspaper in February 2017 and Julian Reichelt took over the position as editor-in-chief. The paper increasingly started painting a picture of refugees as criminals on the tabloid's front page [@Niggemeyer2018Bild; @DLF2018Reichelt]. Headlines like "I killed 40 people and want asylum" increasingly dominated the migration coverage of the newspaper. In a speech months before he took over the position as chief editor, Reichelt outlined his motivation for such a shift in migration coverage: "I can assure you: nothing has hurt [*Bild*] economically as much as our clear, humane, empathetic stance in the refugee crisis" \footnote{Reichelt in a speech at Deutschlandfunk's conference "Formate des Politischen 2016": \url{https://vimeo.com/190347766}}. While he expressed his support for the decision to take this stance at the time, he argued that the German media is self-censoring and generally shows too little tolerance towards anti-immigration attitudes, thereby excluding those holding such views from political discourse.

This case presents a unique case to study the effects of media content on public opinion. As I will show below, the emphasis of crime strongly increased in *Bild*'s migration coverage following Reichelt's takeover. The change of editor itself was not discussed in the media, which means any opinion changes among readers can only be the result of the changing content [see @Spirig2020]. Additionally, the timing of the editorial change is potentially exogenous, given the pressure from allegations against Diekmann. In summary, *this case is as close as possible to a field experiment in which a specific consideration of migration coverage is amplified in the coverage of one newspaper, but not others*.

In the following sections, I will outline a framework for the measurement of emphasis frames in communication and showcase the increasing emphasis of crime in *Bild*'s migration coverage (the treatment). Subsequent sections will describe the panel data and variables to measure frames in thought (namely migration attitudes and their correlation with attitudes about crime) and define the difference-in-difference estimator. I will close with a discussion of the expected experimental effect size and minimal effects of interest to provide baselines for comparison of the estimator.

## Measuring Frames in Communication

To measure migration framing in the news, I collected 2.5 million newspaper articles from the websites of the most important German broadsheets **Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt* and the major German tabloid *Bild* for the period 2013-2019 (for the market reach of each outlet, see table 1 in the appendix). Following the value-expectancy model, I identify crime frames in migration coverage in a two-step process: first, I use supervised machine learning to identify content about migration. Second, I identify content about crime *within* migration coverage by applying another supervised classifier. This approach closely resembles the value-expectancy model outlined in section \@ref(framing-effects), as I first identify coverage about the *issue*, before identifying the considerations emphasized in the discussion of this issue.

To identify whether an article is about migration, I employ supervised machine learning. As migration content is rare, and sufficient training data needs to be available to train functional classifiers, articles cannot be selected randomly for annotation\footnote{If migration content made up about 3% of all articles and the sample were selected randomly, one would find around 30 migration articles per 1000 articles, which provides rather limited information about the class of interest and results in worse recall of the classifier, as the best guess in highly imbalanced data is simply the most common outcome.}. Instead, I first construct a dictionary of terms related to migration. I use dictionary extension based on German GloVe word-embeddings\footnote{Downloadable from \url{https://deepset.ai/german-word-embeddings}.} to construct a comprehensive dictionary, and apply it to the articles. Based on the relative share of migration words in an article, I draw a stratified sample of 300 articles (100 from articles with no migration terms, 100 from the quarter with the highest share of migration terms and 100 from the remaining articles with relative frequencies of migration-related terms in between these two groups) for each newspaper for a total of 1,800 papers. Then, a coder hand-coded these articles, assessing whether their main topic is related to migration\footnote{A precise description of the classification process for migration and crime-related articles, including sampling dictionaries, instructions for coders, and preprocessing steps, can be found in appendix 1.2.}.

Using this sample, a BERT transformer model\footnote{\url{https://huggingface.co/bert-base-german-cased}} is fine-tuned on a random subset of 1,400 annotated articles (training set) with a validation set of 200 articles. After fine-tuning, the model correctly classifies 95.5% of a test set of 200 articles (F1: 0.94, recall: 0.93, precision: 0.95). This classifier is then used to annotate all 2.5 million newspaper articles. For the period from 2013 to 2019, around 90,000 (3.6%) are identified to treat the issue of migration.

To identify migration coverage containing the crime consideration and thereby associating migration with crime, I first fine tune a BERT classifier for German language in a similar fashion as above, this time with coverage about crime as the outcome of interest. Using a training set of 1400 articles, a validation set of 200 and a test set of 200 articles, the classifier reaches a very good performance with an F1 score of 85.7%. I then apply this classifer to identify the approximately 90,000 articles about migration identified by the first classifier. About 7% of all migration coverage consists of articles about some form of crime\footnote{See appendix 1.2 for more information about the classifier, training process and data.}. The share of migration content devoted to news about crime allows me to assess the prominence of the consideration of crime within migration coverage. Exemplifying the narture of the treatment, table \@ref(tab:exampleArticles) displays the headlines of the five migration articles within *Bild* which were identified to discuss crime with the highest likelihood. All articles refer to crimes of migrant groups, with two referring to violence in refugee homes, two discussing police raids regarding asylum fraud, and one discussing a police report about the sexual assaults surrounding new years eve in cologne.

```{=tex}
\begin{table}
\centering
\begin{tabular}{|p{12cm}|}
\hline
Final new years eve report of Cologne police: male groups identified \\ \hline
Police searching for Northern-african offender: asylum-raid in Dortmund! \\ \hline
Search in refugee home - mega-raid addressing asylum fraud \\ \hline
Two groups attacking each other - again bloody conflict in refugee shelter \\ \hline
Cabin fever! Violence! Mass brawls! This is behind the increase in refugee clashes \\ \hline
\end{tabular}
\caption{Headlines of five migration articles most likely to concern crime, according to BERT crime classifier. Translation by author.}
\label{tab:exampleArticles}
\end{table}
```

The left panel of figure \@ref(fig:treatment) shows the share of migration coverage devoted to crime news (solid, red line), once for Bild and once for all other newspapers (dashed, black line). As we can see, *Bild*'s attention to crime news in its migration coverage substantially increased directly following the takeover of Julian Reichelt, while it focused less on the issue preceding the editorial change\footnote{Note that this data is corrected for large changes in the overall number of articles being published by Bild. These chacnges can be traced back to a changing share of content from the German news agency dpa, which provides services to quickly distribute breaking news similar to the Associated Press. Estimates including content from dpa indicate a change in attention to crime of even larger size (6 percentage points), as can be seen in appendix 1.4.}. The trends run parallel to each other preceding the treatment. The lower attention to crime in 2015 and the increase in 2016 is in line with prior research [@Maurer2019]. The right-hand panel shows difference-in-difference estimates of the crime emphasis in migration coverage of one newspaper compared to all others, before and after the editorial change in *Bild*. One can see that *Bild* was the only newspaper which substantially changed its emphasis of the frame, increasing the share of articles devoted to crime by around 5 percentage points, while other newspapers maintained their levels of attention.

```{r treatment, fig.cap="Estimated change in attention to crime content in migration coverage, Bild vs. other newspapers. Black ticks in left panel indicate survey waves."}

TreatmentTrendPlot(dpa_corrected = T) + 
  TreatmentDiDPlot(dpa_corrected = T)

```

## Measuring Frames in Thought

In order to assess the impact of this change in framing on public opinion, it is necessary to use data on citizens' immigration attitudes, as well as their news consumption. The 2017 Election Panel by the German Longitudinal election study contains this data. It consists of a total of 15 waves from 2016-2020, with 10,000 - 20,000 respondents per wave [@GLES2017Panel]. Thirteen of these waves contain questions on immigration attitudes, asking respondents whether immigration of foreigners should be liberalized or  restricted. Responses were recorded on a seven-point Likert scale. This variable was centered on zero ($-3$ - liberalize, $3$ - restrict; the precise wording in the survey can be found in appendix 3.2).

The panel also contains a question on newspaper consumption, which was asked in seven waves. The question provides respondents with a list of the six major daily newspapers plus an option "another daily newspaper", and asks whether they had consumed the paper in print or read articles from their website, and if so, how many days in the past week.

## Estimation

To assess the precise impact of increased attention to crime in migration coverage, I will present evidence from a *difference-in-differences* (DiD) estimator to show the effect of the editorial change - and the related content shift - on migration attitudes:

$$
y_{iw} = \alpha + \beta_1*Post_w + \beta_2 * Post_w * BildReader_i + \phi_w + \rho_i + \epsilon_{it} 
$$

The dependent variable $y_{iw}$ indicates respondent $i$'s migration attitude in a given survey wave $w$, measured on the Likert scale described above. The conditioning variable $BildReader_i$ is a simple binary variable indicating whether respondents read *Bild* in the past week and is measured in the pre-treatment wave. $Post_w$ indicates whether an interview took place preceding or following the editorial change. The estimator of interest is $\beta_2$, which indicates the change in migration attitudes of *Bild* readers following the editorial change, controlling for time-constant ($\rho_i$) and wave-specific ($\phi_w$) factors with fixed effects, as well as general pre-post shifts in migration attitudes ($Post_w$). Note that the pre-treatment differences of treatment and control group are corrected for in the individual fixed effects, as the groups are constant over time (reaedrship is only assessed pre-treatment).

## Expected Effect Size

To provide a baseline expectation regarding the effect from experimental work, it is useful to consider the expected effect size at this point. Despite the abundance of framing effects studies, there is no common standard to assess the magnitude of framing effects. Even the correct measurement of the magnitude is a contested question, as different control groups can be compared [@Druckman2001; @Chong2007a, 109f for a discussion]. Additionally, framing effects differ based on the polarization and salience of the issue [@Lecheler2009b], repeated exposure [@Chong2007competitiveFraming], the sender [@Slothuus2010], political knowledge [@Chong2007b], as well as the reference of certain groups [@Nelson1996]. Generally, reported effect size around 30% of the scale are not uncommon [@Slothuus2010], sometimes even over 40% [@Chong2007a, 104], but most results lie in between 10% and 25% of the scale when comparing opposing frames pushing respondents in opposite directions\footnote{As many studies do not include a control group, this is the most comparable metric.} [@Lecheler2009b; @Nelson1997Psychology; @Nelson1997Rally; @Slothuus2008; @Slothuus2010]. As experimental treatments are likely designed in order to elicit strong responses, and given biases towards null effects in the production of scientific knowledge [see e.g. the recent debate regarding nudging effects: @Maier2022], reported effects likely display a selection bias towards strong treatments. The treatment can be considered rather strong here, as the crime consideration is associated with a strongly negative evaluation and the relative increase in the prevalence of this content is large \footnote{5 percentage point increase compared to pre-treatment share of 8.36 percent in Bild, a 60 percent increase.}. Given these considerations, I expect an effect of around 10% of the scale, or 0.6 on the seven-point scale\footnote{As the scale runs from one to seven, it spans six points wide.}, which represents a conservative estimate compared to reported experimental effects.

As suggested by @Lakens2017, I also compare the estimated effect to equivalence bounds indicating the smallest effect size of interest (SESOI, indicated by dotted lines in the figures below) in order to detect possible null effects. I define the SESOI at a 2.5% change, or 0.15 on the seven-point scale, which represents a fraction of the conservative experimental estimate and sets a fairly low bar given the strong treatment. This SESOI can be used to define equivalence bounds. Any effect estimated to lie within these bounds with statistical significance (i.e. a 95%-confidence interval in-between the positive and negative effect of this size) is too small to constitute a meaningful effect, as the hypothesis that the effect reaches any size of interest can be rejected [see also @Peyton2020].

# Results

The following section discusses the results. I will first present the above-discussed estimate of the effect on immigration attitudes and the association of immigration with crime attitudes. Then, I will assess the impact across time and on related variables to assess the robustness of the estimation. The last section will trace the key assumptions in the translation of experimental estimates discussed in section \@ref(framing-limits).

## Effect on Migration Attitudes

```{r singlemodel}


gles_p_long <- 
  fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
  as_tibble()

postdate <- as.Date("2017-02-01")
title <- "Mean migration attitude post-Reichelt takeover"

gles_p_long["dv"] <- gles_p_long["1130_clean"]
    
single_model <- 
  fixest::feglm(dv ~ post*treat | lfdn + wave_ctrl, 
                data = 
                  gles_p_long %>% 
                  filter(!is.na(dv)) %>% 
                  mutate(
                    wave_ctrl = 
                      ifelse(
                        wave %in% unique(.$wave[c(1,2)]),
                        "reference",
                        wave
                      )
                  ) %>% 
                  select(dv, post, treat, lfdn, wave_ctrl),
                cluster = c("lfdn", "wave_ctrl"))

ATT <- single_model$coefficients[["postTRUE:treatTRUE"]]
t_ATT <- single_model$coeftable["postTRUE:treatTRUE", "t value"]
p_ATT <- single_model$coeftable["postTRUE:treatTRUE", "Pr(>|t|))"]

```

Figure \@ref(fig:singleplot) visualizes the effect of the change in framing on immigration attitudes. Dashed vertical lines indicate the expected effect from the experimental literature. The dotted lines indicate the equivalence boundaries. If the 95% interval is contained within these boundaries, the hypothesis that the estimate is larger than the SESOI can be rejected. The point estimate indicates a `r round(ATT, 3)`-point change among Bild readers following treatment (*t =* `r round(t_ATT, 2)`, *p =* `r round(p_ATT, 2)`), which is around `r round(ATT*100/0.6)`% of the expected effect of 0.6. The 95% confidence interval also contains values far smaller than the SESOI of 0.15 but clearly include the vertical solid red line indicating no change. Surprisingly, the model suggests a clear null effect.

```{r singleplot, fig.cap="Effect of change in framing on migration attitudes; difference-in-differences estimate. Dashed vertical lines indicate conservative experimental effect (0.6, baseline expectation), dotted vertical lines indicate minimal relevant effect (0.15). Full model visible in Appendix XX.", fig.height=2}

DiDPlot(multi = F, scaled = "raw", 
        theoretical_effect_size = 0.6, boundary_share = 0.25)


```

## Effect on The Association of Crime and Migration Attitudes

As outlined above, framing theory suggests that increased exposure to a specific consideration about an issue leads to stronger association of the issue with this consideration. In the present case, this should mean that the correlation of attitudes on immigration with attitudes about crime should increase. The GLES Panel data contains a variable asking respondents whether "the state's capabilities to fight crime should be extended, even if that would entail more surveillance", asked in three waves overlapping with the migration attitude question. 

Figure \@ref(fig:corplot) shows the correlation of crime- and migration attitudes in treatment (Bild-readers in pre-wave) and control group (never Bild-readers), pre- and post-treatment. I added a counterfactual, applying the change in the control group to the treatment group, for easier interpretation. As we can see, the treatment group actually saw a *smaller* increase in the correlation of crime and migration attitudes than the control group, *despite weaker pre-treatment association*. Following [@Nelson1996], table \@ref(tab:cortable) regresses immigration attitudes on attitudes towards crime and investigates whether this association is generally different between the two groups\footnote{These differences are however in the opposite direction as the (substantial) differences in the descriptive correlations outlined in the plot. I am currently not sure how to interpret this.}, changes post-treatment, and whether it changes more in the treatment group using interaction terms. I find minor differences between the groups, but no significant difference when interacted with the DiD-term - respondents do not seem to associate crime more strongly with migration following the change in migration coverage in *Bild*.

```{r corplot, fig.width=8, fig.height=4, fig.cap = "Correlation of crime and migration attitudes in treatment and control group, pre- (wave 1) and post-treatment (waves 3 \\& 13)."}

MigCrimeCorPlot()

```

```{r cortable}

MigCrimeCorTable()

```

[explain why this is done, and why constituent terms are not interesting - only the change in association of crime attitude and dependent variable is of interest, we are not trying to explain variation in the dependent variable! (which is also why R2 doesn't matter here)]

## Robustness

### Effect across time

If readers only perceive the change in content across longer time periods, the effect should slowly unfold across time. If that is the case, initial absence of change might bias the estimates downward and thereby mask an effect. To assess whether an effect develops over time, figure \@ref(fig:migwaves) assesses the effect within split-samples for each post-wave compared to the pre-treatment wave. This allows the assessment of heterogeneous treatment effects across time. The black dots with associated confidence intervals indicate the estimated effect for each wave. The horizontal dashed line indicates the expected effect based on experimental evidence (0.6), whereas the dotted horizontal line indicates the SESOI of 0.15. The vertical (red) dashed line indicates the timing of the editorial change, whereas the dotted (orange) vertical line indicates the timing of the strong increase in crime framing in June 2017, several months after the takeover by Reichelt (see figure \@ref(fig:treatment)). Over the course of the entire year 2017, the effect is clearly smaller than the SESOI, and includes zero. However, estimates for waves 7 and 8 in late 2018 and mid-2019 - more than one and a half years after the editorial change - showcase effects statistically different from zero, and including the SESOI boundary. Note however that the effect is still tiny, with a point estimate smaller than a 0.1 on the seven-point Likert scale, as well as an upper boundary just above the SESOI at ??. The waves in late 2019 and early 2020 have point estimates at similar lower levels (??, ??), but include zero again. Overall, this suggests an effect that remains below an effect size of minimal relevance.

```{r migwaves, fig.cap="Effect of Change in Framing on Immigration Attitudes across Waves. Dashed (black) horizontal lines indicate conservative experimental effect (0.6, baseline expectation), dotted horizontal lines indicate minimal relevant effect (0.15). Dashed (red) vertical line indicates effect of Reichelt takeover, dotted (orange) line timing of change in coverage. Full models visible in Appendix XX."}

# add 0.9 confidence bar

DiDByWavePlot(theoretical_effect_size = 0.6, boundary_share = 0.25)


```

### Effect on other alternative dependent variables

While immigration attitudes remain unaffected, it might well be that an increased exposure to crime framing affects other variables. For example, increased attention to crime within migration coverage might increase individual perceptions of the importance of migration, despite not changing attitudes, or raise concerns about the integration rather than the immigration of migrants. Similarly, support for the radical-right *AfD* as owner of the migration issue could increase as a result of increased exposure to crime frames. All variable descriptions and models can be found in the appendix. 

Figure \@ref(fig:multidv) displays standardized effects of the change in newspaper framing on immigration attitudes (as reference) and three related dependent variables, namely integration attitudes, the likelihood to report migration as the most important problem facing the country, as well as thermometer scores for the radical-right AfD (see Appendix ?? for precise variable descriptions). Dotted lines indicate a 0.2 standard deviation change, which has been defined as the standardized equivalence boundary in existing research [@Peyton2020, 599]. All estimated effects are smaller in size than 0.05 standard deviations and associated 95%-confidence intervals contain zero. This means we can reject the hypothesis of meaningful effect size, but cannot reject that the estimate is statistically different from zero. All estimates suggest a clear null effect.

```{r multidv, fig.cap="Standardised effect of change in framing on alternative dependent variables. Dotted vertical lines indicate minimal relevant effect (0.2 SD). Full models available in Appendix XX."}

# add 0.9 confidence bar

DiDPlot(multi = T, scaled = T, 
        theoretical_effect_size = 0.2) # 0.2 SD suggested by Peyton 2020, 599

```

## Assumptions in the Translation of Experimental Estimates

### Selective Exposure

```{r selectionModel}

m_sel <- SelectionModel()

```

As the migration framing in Bild becomes more conservative, this could also lead readers with more liberal migration attitudes to stop reading the newspaper, as they avoid information challenging their views. Figure \@ref(fig:selection) shows the share of initial readers that report reading Bild at later stages. The three different lines describe three different groups, based on their initial migration attitude. If readers reacted by selective exposure, one would expect that liberal readers' share would drop more significantly than conservative reader's share, as they actively select out of the newspaper. As one can see, that is not the case. Liberals' and conservatives' share of readers track each other closely, with those reporting liberal migration attitudes in the first wave even reporting to read Bild at *higher* shares than conservatives in later waves. What is interesting is that those reporting neutral migration attitudes seem to be more inclined to leave the newspaper: Neutral readership declines to a level of 57%, around 5 percentage points below the share reported by liberals (62%) and 3pp below the level of conservatives (60%). Regressing individual choice to read *Bild* in later waves on initial reported migration attitudes within the subsample of initial *Bild* readers shows a `r round(m_sel$coefficients[["init_mig_groupsNeutral"]], 2)*-100`% lower chance to report Bild readership among initial neutral readers, compared to liberal readers ($p =$ `r round(summary(m_sel)$coefficients["init_mig_groupsNeutral", "Pr(>|t|)"], 3)`), whereas there is no significant or substantial difference for conservative readers. Surprisingly, *Bild* readers reporting centrist immigration attitudes select out of the newspaper at higher rates than both conservative or liberal readers, whereas there is no meaningful difference between the latter two.

```{r selectionPlot, fig.cap="Share of initial Bild readers reporting readership in later waves by initial migration attitude. Dashed (red) vertical line indicates editorial change."}

OutSelection()

```

### Attitude Crystallisation

```{r MigChange, fig.cap="Change in individual immigration attitudes 2016-2018, compared to 2014-2016. Data taken from the GLES Longterm Panel (SOURCE)."}

MigChangePlot()

MigChangeTable <- MigChangePlot(return_table = T)

```

As readers did not react by selecting out of the newspaper, the question emerges *why* readers did not react to the change in coverage. A possible explanation is that individuals informed themselves about the issue and formed an attitude once the issue emerged, in this case in 2015 during the large migratory movements in Europe. If that were the case, opinions should change more from 2014 to 2016 compared to the 2016-2018 period. Figure \@ref(fig:MigChange) shows this statistic using GLES Longterm Panel data [SOURCE]. The top panel shows the absolute change in migration attitudes from 2014-2016. That is, if a respondent held an attitude of 3 (leaning conservative) on the ten-point scale in 2014 and moved to 2 in 2016, their migration attitude would change by 1. Immigration attitudes in the GLES sample shifted on average by `r round(MigChangeTable["2014-2016",][["change_mean"]], 2)` from 2014 to 2016 (lower 95% confidence interval `r round(MigChangeTable["2014-2016",][["change_lower"]], 2)`, upper `r round(MigChangeTable["2014-2016",][["change_upper"]], 2)`), while they shifted significantly less in the period 206-2018 (`r round(MigChangeTable["2016-2018",][["change_mean"]], 2)`; [`r round(MigChangeTable["2016-2018",][["change_lower"]], 2)`, `r round(MigChangeTable["2016-2018",][["change_upper"]], 2)`]).

cite Lecheler et al, Druckman2012; Druckman2012Bias; X & Arceneaux here showing that individuals are resistant to persuasion on high-importance issues and that timing/pretreatment matters

It becomes apparent that individual migration attitudes stabilised after 2015. This evidence is in line with the idea that migration attitudes were only responsive in 2015, when the newspaper did not follow other tabloids in their aggressively negative portrayal of refugees and their impact on society at large. When the newspaper changes its migration coverage one and a half years later, the critical window of opportunity seems to have closed, as migration attitudes had crystallized.

### Crowding Out

# Conclusion: Windows of Opportunity for News Framing Effects

The presented results are robust evidence that, despite an over 70% increase of the emphasis of crime in migration content of Germany's largest newspaper, its readers' migration attitudes remained surprisingly unaffected. Effect estimates remain below minimal thresholds across time. Related dependent variables such as integration attitudes, reporting migration as the most important problem, and support for the radical-right AfD do not deviate from those of other readers. Migration attitudes are not increasingly associated with crime attitudes in this group, nor are liberal Bild readers more likely to stop reading the newspaper, nor conservative non-readers more likely to report reading it.

These findings substantially question the external validity of experimental framing studies. While it is well-established that exposure to single frames can substantially affect political attitudes in survey- and laboratory experiments, this does not seem to easily translate into real world contexts.

Several potential explanations for this difference come to mind. The most likely is certainly selective exposure. Although no evidence for selective exposure on the outlet level could be found, readers might still select content *within* the outlet - that is, they skip articles contradicting their worldview or simply do not engage with the content on a cognitive level. Alternatively, the diversity of contemporary media environments might expose individuals with so many different frames that political attitudes are ultimately stabilized. The framing of individual outlets is crowded out by the many outlets which are consumed.

While these findings substantially question evidence from experimental framing studies, they are generally good news for democracy: even when outlets try, they cannot simply manipulate their audience's political attitudes with a snap of their finger. Worries about the undermining of democracy through the takeover of partisan news outlets might be overstated, as consumers either seem to hold a critical distance to their news outlets or consume content from so many outlets that a single one has not much influence. Descriptive data about American news diets supports this interpretation [@Guess2021a].

Despite the unique case and the extensive efforts to isolate the effect of the documented change inframing, this study suffers from several limitations regarding the generalizabilty of the case at hand. First, the immigration issue was already highly salient for one and a half years when Reichelt took over *Bild*. This means that attitudes have possibly crystallized as the result of personal reasoning, exposure to information, or cues from one's preferred party. Second, while tabloids are often seen as manipulators of public opinion [@Foos2022], they also contain less political content and might be taken less seriously when they write about politics. Readers from other outlets might react differently. Lastly, Bild readers differ from other readers in many ways, among others they are more conservative and less knowledgeable about politics (see Appendix ??). Readers of other outlets might react differently to increased exposure to crime frames.

[add: no randomisation of treatment!! plus adapt to new evidence regarding attitude stability]

This study offers several takeaways for future research. First, and most importantly, the study suggests caution in the generalization of experimental results to the real world. More observational research of framing effects would help in the mapping out of scope conditions for framing effects. The present study presented one approach how this can be done. On the other hand, experimental research could try to explore external validity issues further, assessing the existence of 'crowding out' effects, as well as conditions for and types of selective exposure.

\pagebreak

# Resources
